---
title: "Live Demo VT CMDA Capstone"
author: "Cara Anderson, Sarah Hebert, Nicole Major"
date: "November 8, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First we will set up our R environment by downloading 5 different librarys. The important one for TidyText is TidyText.
```{r}
library(readtext)
library(ggplot2)
library(tidytext)
library(tidyr)
library(dplyr)
library(textdata)


```

Now we can import the data. 
```{r}
#Set the workpath
wp = "set your workpath here to go into the negative folder"
negReviews <- readtext(paste0(wp, "/*"))
negReviews <- cbind(negReviews, "negative")
names(negReviews) <- c("Document", "IMDB_Review", "Sentiment")

wp = "set your workpath here to go into the positive folder"
posReviews <- readtext(paste0(wp, "/*"))
posReviews <- cbind(posReviews, "positive")
names(posReviews) <- c("Document", "IMDB_Review", "Sentiment")

reviews <- rbind(negReviews, posReviews)
View(reviews)
```

Now we will turn the data into tidy data
```{r}
#Transform to tidy data
reviews_df <- tibble(line = 1: nrow(reviews), 
                     Review = reviews$IMDB_Review, 
                     Sentiment = "Neutral")

tidyReviews <- reviews_df %>% 
  mutate(linenumber = row_number()) %>%
    ungroup() %>% unnest_tokens(word, Review)

#Typically want to remove stop words but sometimes this will get rid of that enture data point (prominent in Twitter)
tidyReviews <- tidyReviews %>% anti_join(stop_words)

View(tidyReviews)
```

Now we will look at the bing lexicon
```{r}
#Bing sentiments
bing <- tidyReviews %>% inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()

#Plots top 10 words that contribute to a negative/positive sentiment

bing %>% group_by(sentiment) %>% top_n(10) %>% ungroup() %>%
  mutate(word = reorder(word, n)) %>% ggplot(aes(word, n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") + 
  labs(y = "Contribution to sentiment", x = NULL) + 
  coord_flip()
```

Now we will look at the different lexicons. First we will use the inner_join method with each of the differenct lexicons. 
```{r}
#Gets afinn sentiments
afinn <- tidyReviews %>% inner_join(get_sentiments("afinn")) %>%
  group_by(index = linenumber %/% 1) %>%
  summarize(sentiment = sum(value)) %>%
  mutate(method = "AFINN")

#Combines bing and nrc sentiments
bing_and_nrc <- bind_rows(tidyReviews %>% inner_join(get_sentiments("bing")) %>%
                            mutate(method = "Bing"), tidyReviews %>% inner_join(get_sentiments("nrc") %>%
                                                                                  filter(sentiment %in% c("positive", "negative"))) %>%
                            mutate(method = "NRC")) %>% count(method, index = linenumber %/% 1, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)
```

Finally, we will plot the differences.
```{r}
#Plot the differences
bind_rows(afinn, bing_and_nrc) %>% ggplot(aes(index, sentiment, fill = method)) + 
  geom_col(show.legend = FALSE) + 
  facet_wrap(~method, ncol = 1, scales = "free_y")
```